A Comparison of Parallel Graph Processing Implementations

### 2017-05-15 papers/publication/paper-pollard.tex

As with the graph processing systems, this approach is not specific to a particular algorithm; measuring the execution time, data structure construction time, and power consumption can be applied easily to other algorithms.

>>>>

This approach is not specific to a particular algorithm; measuring the execution time, data structure construction time, and power consumption can be applied easily to other algorithms. We select some representative algorithms here to demonstrate the process, which we hope will motivate others to use
the framework to add more algorithms.
